### 2017-01-03 paper/evaluation.tex
Fixed existing macro

\newcommand{\SubjCnt}{411}

A Maven project may contain several submodules with multiple
\emph{pom.xml} files. We considered only projects with a
\emph{pom.xml} file located in the root directory.  As of December
30th 2016, our search criteria returned 615 subjects. From the 615
downloaded projects, 46 were not Maven projects, 27 were unable to
fetch all dependencies (\eg, due to the usage of a private library),
and 131 were in an unstable revision. Our final set consists in
\SubjCnt{} subjects.

@@

To evaluate the frequency of time-consuming regression tests, we
considered the \SubjCnt{} subjects from Section~\ref{sec:subjects} and
compared the elapsed time to run their tests.
Figure~\ref{fig:mvn-execution} shows the commands used in our script
to test each subject. The main loop (lines 6-12) iterates over the
list of subjects and invokes Maven in separated steps (lines 8-10). To
avoid inflating the measured time, we first compile the source and
test files (line 8), fetch all dependencies (line 9) and later, we run
the tests in offline mode (line 10) to avoid package updates. In
addition we randomly selected 100 Maven logs to inspect and identify
non-related tasks (\eg, \emph{javadoc} generation and static
analysis). We created a list of plugins (lines 1-4) to ignore them
during the test execution.  Finally, we use a simple regular
expression over the test output to extract the elapsed time (line 13).
We executed this experiment \Fix{X} times in our dedicated server
remotely via SSH with the operating system running only essential
services (\eg, the SSH server).

>>>>

A Maven project may contain several submodules with multiple
\emph{pom.xml} files. We considered only projects with a
\emph{pom.xml} file located in the root directory.  As of December
30th 2016, our search criteria returned 615 subjects. From the 615
downloaded projects, 46 were not Maven projects, 27 were unable to
fetch all dependencies (\eg, due to the usage of a private library),
and 131 were in an unstable revision. Our final set consists in
\numSubjs{} subjects.

@@

To evaluate the frequency of time-consuming regression tests, we
considered the \numSubjs{} subjects from Section~\ref{sec:subjects} and
compared the elapsed time to run their tests.
Figure~\ref{fig:mvn-execution} shows the commands used in our script
to test each subject. The main loop (lines 6-12) iterates over the
list of subjects and invokes Maven in separated steps (lines 8-10). To
avoid inflating the measured time, we first compile the source and
test files (line 8), fetch all dependencies (line 9) and later, we run
the tests in offline mode (line 10) to avoid package updates. In
addition we randomly selected 100 Maven logs to inspect and identify
non-related tasks (\eg, \emph{javadoc} generation and static
analysis). We created a list of plugins (lines 1-4) to ignore them
during the test execution.  Finally, we use a simple regular
expression over the test output to extract the elapsed time (line 13).
We executed this experiment \Fix{X} times in our dedicated server
remotely via SSH with the operating system running only essential
services (\eg, the SSH server).
